---
editor_options: 
  markdown: 
    wrap: 72
---

------------------------------------------------------------------------

Install packages

```{r}
install.packages("ggplot2")
install.packages("dplyr")
install.packages("broom")
install.packages("ggpubr")
install.packages("tidyverse")
```

load the packages

```{r}
library(ggplot2)
library(dplyr)
library(broom)
library(ggpubr)
library(tidyverse)
library(readr)
```

# Linear Regression with numeric VI

## Step 1: Load the data into R

```{r}
# Load the database
library(readxl)
data_depression <- read_excel("base_depresion_en_medicos_-_corregida.xlsx")
View(data_depression)
summary(data_depression)

library(readxl)
data_rendimiento <- read_excel("base_rendimiento_academico.xlsx")
View(data_rendimiento)
```

## Step 3: Explore outcome variable (must be numeric)

We checked if the independient variable `nota` (VI) is numeric

```{r}
glimpse(data_rendimiento$nota) #Numeric
glimpse(data_rendimiento$edad)
```

## Step 4: Make sure data assumptions

#### A. Linearity

```{r}
plot(nota ~ edad, data = data_rendimiento)
```

#### B. Independence of observations

Teoricamente se entiende que las variables son independientes

```{r}

```

#### C. Normality

```{r}

hist(data_rendimiento$edad)
# Se puede evaluar la normalidad por  QQplot, Kurtosis
```

## Step 3: Perform the linear regression analysis

```{r}
rendimiento_lm <- lm(nota ~ edad, data = data_rendimiento)

summary(rendimiento_lm)
```

## Step 4: Check the homocedasticity

```{r}
par(mfrow=c(2,2))
plot(rendimiento_lm)
par(mfrow=c(1,1))
```

## Step 5: Perform a graph to visualize the results

## Step 6: Report and interpret your results

# Multiple Regression with numeric VI

## Step 1: Load the data into R

```{r}
# Load the database
library(readxl)
data_depression <- read_excel("base_depresion_en_medicos_-_corregida.xlsx")
View(data_depression)
summary(data_depression)

library(readxl)
data_rendimiento <- read_excel("base_rendimiento_academico.xlsx")
View(data_rendimiento)
```

## Step 3: Explore outcome variable (must be numeric)

We checked if the independient variable `nota` (VI) is numeric

```{r}
glimpse(data_rendimiento)
glimpse(data_rendimiento$nota) #Numeric
glimpse(data_rendimiento$edad) # Numeric
glimpse(data_rendimiento$promsecu) #Numeric
```

## Step 4: Make sure data assumptions

#### A. Linearity

```{r}
plot(nota ~ edad, data = data_rendimiento)
plot(nota ~ promsecu, data = data_rendimiento)
```

#### B. Independence of observations

Teoricamente se entiende que las variables son independientes

```{r}
library(car)
cor(data_rendimiento$edad, data_rendimiento$promsecu)
vif(m_rendimiento_lm)

```

#### C. Normality

```{r}

hist(data_rendimiento$nota)
# Se puede evaluar la normalidad por  QQplot, Kurtosis
```

## Step 3: Perform the linear regression analysis

```{r}
m_rendimiento_lm <- lm(nota ~ edad + promsecu + vivesolo, data = data_rendimiento)

summary(m_rendimiento_lm)
```

## Step 4: Check the homocedasticity

```{r}
par(mfrow=c(2,2))
plot(m_rendimiento_lm)
par(mfrow=c(1,1))
```

## Step 5: Perform a graph to visualize the results

```{r}
print(m_rendimiento_lm)


# Get the Intercept and coefficients as vector elements.
cat("# # # # The Coefficient Values # # # ","\n")

a <- coef(m_rendimiento_lm)[1]
print(a)

Xedad <- coef(m_rendimiento_lm)[2]
Xprom <- coef(m_rendimiento_lm)[3]

print(Xedad)
print(Xprom)
```

```{r}
plotting.data <- expand.grid(
  edad = seq(min(data_rendimiento$edad), max(data_rendimiento$edad),lenght.out=30),
  promsecu = seq(min(data_rendimiento$promsecu), mean(data_rendimiento$promsecu)))
                            
  
  
plotting.data$predicted.y <- predict.lm(m_rendimiento_lm, newdata=plotting.data)

plotting.data$promsecu <- round(plotting.data$promsecu, digits = 2)

plotting.data$promsecu <- as.factor(plotting.data$promsecu)


nota.plot <- ggplot(data_rendimiento, aes(x=edad, y=nota)) +
  geom_point()

nota.plot

```

## Step 6: Report and interpret your results

# Linear Regression with categorical VI

Step 1: Load the data into R

Step 2: Order each variable

Step 3: Explore outcome variable (must be categorical)

Step 4: Make sure data assumptions

Step 5: Perform a graph to visualize the results

Step 6: Report and interpret your results

# Multiple Regression with categorical VI

## Step 1: Load the data into R

We checked if the data has the independent variable `income` (*X*) and
dependent variable `happiness` (*Y*)

```{r}
# Load the database
income_data <- read_csv("income.data.csv")
View(income_data)
summary(income_data) #numeric summary
```

## Step2: Make sure the data meet the assumptions

### Assumptions

#### A. Linearity

```{r}
par (mfrow=c(2, 2))
plot (income_data)
plot(happiness ~ income, data= income_data)
```

#### B. Independence of observations

```{r}

```

#### C. Normality

```{r}
hist(income_data$happiness)
```

#### D. Homoscedasticity

```{r}

```

## Step 3: Perform the linear regression analysis

```{r}
income_happiness_lm <- lm(happiness ~ income, data = income_data)

summary(income_happiness_lm)
```

## Step 4: Check the homocedasticity

```{r}
par(mfrow=c(2,2))
plot(income_happiness_lm)
par(mfrow=c(1,1))
```

## Step 5: Perform a graph to visualize the results

### 1. Plot the data in default graph

```{r}
income_graph<-ggplot(income_data, aes(x=income, y=happiness))+
                     geom_point()
income_graph
```

### 2. Add the linear regression

```{r}
income_graph <- income_graph + geom_smooth(method="lm", col="black")

income_graph
```

### 3. Add the equation

```{r}
income_graph <- income_graph +
  stat_regline_equation(label.x = 3, label.y = 7)

income_graph
```

### 4. Make it more beautiful

```{r}
# Is only a copy
income_graph +
  theme_bw() +
  labs(title = "Reported happiness as a function of income",
      x = "Income (x$10,000)",
      y = "Happiness score (0 to 10)")
```

## Step 6: Report/Interpret your results
